Mispronunciation Sensitivity Publication Bias for CogSci

### 2018-05-09 CogSci_Publication_bias.Rmd
updated code for response to CogSci reviewers
- changed color to dark blue for age by effect size plot
- changed axis and overall titles for funnel plot

#Now we can actually make the funnel plot.
#Using your original data-frame, map standard error to your x-axis (for now) and Zr to your y-axis
fp_co = ggplot(aes(x = se, y = yi), data = dat_co) +
  #Regression line for the FP asymmetry
  geom_smooth(aes(x = se, y = yi), method = "lm", colour = "darkgrey", alpha = .5, se = FALSE, data = dat_co) +
  #Add your data-points to the scatterplot
  geom_point(size = 2.5, colour="black") +
  #
  #Give the x- and y- axes informative labels
  xlab('Standard Error') + ylab('Hedge\'s g')+
  # make sure both plots have same scale
  # still ylim because we haven't flipped yet
  #coord_cartesian(ylim = c(-1, 2.5))+
  #Now using the 'dfCI' data-frame we created, plot dotted lines corresponding
  #to the lower and upper limits of your 95% CI region
  #And dashed lines corresponding to your 99% CI region
  #Add lines corresponding to 0 and estimate
  geom_line(aes(x = se.seq_co, y = 0), linetype = 'solid', data = dfCI_co) +
  geom_line(aes(x = se.seq_co, y = estimate_co), linetype = 'dashed', data = dfCI_co) +
  geom_line(aes(x = se.seq_co, y = ll95_co), linetype = 'dotted', data = dfCI_co) +
  geom_line(aes(x = se.seq_co, y = ul95_co), linetype = 'dotted', data = dfCI_co) +
  #  geom_line(aes(x = se.seq, y = ll99), linetype = 'dashed', data = dfCI) +
  #  geom_line(aes(x = se.seq, y = ul99), linetype = 'dashed', data = dfCI) +
  #Now plot dotted lines corresponding to the 95% CI of your meta-analytic estimate
  #geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI) +
  #geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI) +
  #Reverse the x-axis ordering (se) so that the tip of the funnel will appear
  #at the top of the figure once we swap the x- and y-axes...
  scale_x_reverse()+
  #Specify the range and interval for the tick-marks of the y-axis (Zr);
  #Choose values that work for you based on your data
  #scale_y_continuous(breaks=seq(-.45,0.8,0.25))+
  #And now we flip the axes so that SE is on y- and Zr is on x-
  coord_flip()+
  #Finally, apply my APA-format theme (see code at end of post).
  #You could, alternatively, specify theme_bw() instead.
  apatheme

#Call the pretty funnel plot
fp_co +   ggtitle("Correct")
#ggsave("figures/FunnelPlot_correct.pdf")

@@

  #Now we can actually make the funnel plot.
  #Using your original data-frame, map standard error to your x-axis (for now) and Zr to your y-axis
  fp_mp = ggplot(aes(x = se, y = yi), data = dat_mp) +
    #Regression line for the FP asymmetry
    geom_smooth(aes(x = se, y = yi), method = "lm", colour = "darkgrey", alpha = .5, se = FALSE, data = dat_mp) +
    #Add your data-points to the scatterplot
    geom_point(size = 2.5, colour="black") +
    #
  #Give the x- and y- axes informative labels
  xlab('Standard Error') + ylab('Hedge\'s g')+
    # make sure both plots have same scale
    # still ylim because we haven't flipped yet
    #coord_cartesian(ylim = c(-1, 2.5))+
    #Now using the 'dfCI' data-frame we created, plot dotted lines corresponding
    #to the lower and upper limits of your 95% CI region
    #And dashed lines corresponding to your 99% CI region
    #Add lines corresponding to 0 and estimate
    geom_line(aes(x = se.seq_mp, y = 0), linetype = 'solid', data = dfCI_mp) +
    geom_line(aes(x = se.seq_mp, y = estimate_mp), linetype = 'dashed', data = dfCI_mp) +
    geom_line(aes(x = se.seq_mp, y = ll95_mp), linetype = 'dotted', data = dfCI_mp) +
    geom_line(aes(x = se.seq_mp, y = ul95_mp), linetype = 'dotted', data = dfCI_mp) +
    #  geom_line(aes(x = se.seq, y = ll99), linetype = 'dashed', data = dfCI) +
    #  geom_line(aes(x = se.seq, y = ul99), linetype = 'dashed', data = dfCI) +
    #Now plot dotted lines corresponding to the 95% CI of your meta-analytic estimate
    #geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI) +
    #geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI) +
    #Reverse the x-axis ordering (se) so that the tip of the funnel will appear
    #at the top of the figure once we swap the x- and y-axes...
    scale_x_reverse()+
    #Specify the range and interval for the tick-marks of the y-axis (Zr);
    #Choose values that work for you based on your data
    #scale_y_mpntinuous(breaks=seq(-.45,0.8,0.25))+
    #And now we flip the axes so that SE is on y- and Zr is on x-
    coord_flip()+
    #Finally, apply my APA-format theme (see code at end of post).
    #You could, alternatively, specify theme_bw() instead.
    apatheme

  #Call the pretty funnel plot
  fp_mp + ggtitle("Mispronunciation")
#  ggsave("figures/FunnelPlot_misp.pdf")

@@

#  jpeg(filename = "figures/Funnel_Plots_Object_Identification.jpg", 
#       width = 600, height = 400, units = "px")

@@

#  dev.off()

>>>>

#Now we can actually make the funnel plot.
#Using your original data-frame, map standard error to your x-axis (for now) and Zr to your y-axis
fp_co = ggplot(aes(x = se, y = yi), data = dat_co) +
  #Regression line for the FP asymmetry
  geom_smooth(aes(x = se, y = yi), method = "lm", colour = "darkgrey", alpha = .5, se = FALSE, data = dat_co) +
  #Add your data-points to the scatterplot
  geom_point(size = 2.5, colour="black") +
  #
  #Give the x- and y- axes informative labels
  xlab('Standard Error') + ylab('Hedge\'s g')+
  # give it a title
    ggtitle("Correct") +
    # make sure both plots have same scale
    # still ylim because we haven't flipped yet
    #coord_cartesian(ylim = c(0.5, 0))+
  #Now using the 'dfCI' data-frame we created, plot dotted lines corresponding
  #to the lower and upper limits of your 95% CI region
  #And dashed lines corresponding to your 99% CI region
  #Add lines corresponding to 0 and estimate
  geom_line(aes(x = se.seq_co, y = 0), linetype = 'solid', data = dfCI_co) +
  geom_line(aes(x = se.seq_co, y = estimate_co), linetype = 'dashed', data = dfCI_co) +
  geom_line(aes(x = se.seq_co, y = ll95_co), linetype = 'dotted', data = dfCI_co) +
  geom_line(aes(x = se.seq_co, y = ul95_co), linetype = 'dotted', data = dfCI_co) +
  #  geom_line(aes(x = se.seq, y = ll99), linetype = 'dashed', data = dfCI) +
  #  geom_line(aes(x = se.seq, y = ul99), linetype = 'dashed', data = dfCI) +
  #Now plot dotted lines corresponding to the 95% CI of your meta-analytic estimate
  #geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI) +
  #geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI) +
  #Reverse the x-axis ordering (se) so that the tip of the funnel will appear
  #at the top of the figure once we swap the x- and y-axes...
  scale_x_reverse()+
  #Specify the range and interval for the tick-marks of the y-axis (Zr);
  #Choose values that work for you based on your data
  #scale_y_continuous(breaks=seq(-.45,0.8,0.25))+
  #And now we flip the axes so that SE is on y- and Zr is on x-
  coord_flip()+
  #Finally, apply my APA-format theme (see code at end of post).
  #You could, alternatively, specify theme_bw() instead.
  apatheme

#Call the pretty funnel plot
fp_co
#ggsave("figures/FunnelPlot_correct.pdf")

@@

  #Now we can actually make the funnel plot.
  #Using your original data-frame, map standard error to your x-axis (for now) and Zr to your y-axis
  fp_mp = ggplot(aes(x = se, y = yi), data = dat_mp) +
    #Regression line for the FP asymmetry
    geom_smooth(aes(x = se, y = yi), method = "lm", colour = "darkgrey", alpha = .5, se = FALSE, data = dat_mp) +
    #Add your data-points to the scatterplot
    geom_point(size = 2.5, colour="black") +
    #
  #Give the x- and y- axes informative labels
  xlab('Standard Error') + 
    # remove y label because it will be combined with the other funnel plot
    ylab('Hedge\'s g')+
    # give it a title
    ggtitle("Mispronunciation") +
    # make sure both plots have same scale
    # still xlim because we haven't flipped yet
    #coord_cartesian(xlim = c(0.5, 1))+
    #Now using the 'dfCI' data-frame we created, plot dotted lines corresponding
    #to the lower and upper limits of your 95% CI region
    #And dashed lines corresponding to your 99% CI region
    #Add lines corresponding to 0 and estimate
    geom_line(aes(x = se.seq_mp, y = 0), linetype = 'solid', data = dfCI_mp) +
    geom_line(aes(x = se.seq_mp, y = estimate_mp), linetype = 'dashed', data = dfCI_mp) +
    geom_line(aes(x = se.seq_mp, y = ll95_mp), linetype = 'dotted', data = dfCI_mp) +
    geom_line(aes(x = se.seq_mp, y = ul95_mp), linetype = 'dotted', data = dfCI_mp) +
    #  geom_line(aes(x = se.seq, y = ll99), linetype = 'dashed', data = dfCI) +
    #  geom_line(aes(x = se.seq, y = ul99), linetype = 'dashed', data = dfCI) +
    #Now plot dotted lines corresponding to the 95% CI of your meta-analytic estimate
    #geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI) +
    #geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI) +
    #Reverse the x-axis ordering (se) so that the tip of the funnel will appear
    #at the top of the figure once we swap the x- and y-axes...
    scale_x_reverse()+
    #Specify the range and interval for the tick-marks of the y-axis (Zr);
    #Choose values that work for you based on your data
    #scale_y_mpntinuous(breaks=seq(-.45,0.8,0.25))+
    #And now we flip the axes so that SE is on y- and Zr is on x-
    coord_flip()+
    #Finally, apply my APA-format theme (see previous).
    #You could, alternatively, specify theme_bw() instead.
    apatheme +
    theme(axis.title.y = element_blank())

  #Call the pretty funnel plot
  fp_mp
#  ggsave("figures/FunnelPlot_misp.pdf")

@@

  jpeg(filename = "figures/Funnel_Plots_Object_Identification.jpg", 
       width = 600, height = 400, units = "px")

@@

  dev.off()
